Figures

### 2018-11-02 code/figures.rmd
Updated draft and associated files
Corrected legend alpha figure 3

# summary(lm(H2alt ~ z, data = res2)) #b = 3.81, R2 = 0.53

@@

ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2",
                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_color_brewer(palette = "Dark2", 
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(I^2," index", sep = "")))

# ggsave("../figures/density-I2.png", dpi = 600, height =  4 , width = 6.47)
```

>>>>

# summary(lm(H2 ~ z, data = res2)) #b = 3.81, R2 = 0.53

@@

ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2",
                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_color_brewer(palette = "Dark2", 
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(I^2," index", sep = ""))) +
  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))

ggsave("../figures/density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
```
